Evaluating the Performance and Energy Efficiency of COSMO-ART, a Coupled Numerical Weather Forecast and Chemical Transport Model

### 2014-04-11 trunk/paper_enahpc14/paper.tex
restructures paper; improves contents

\keywords{High performance computing  \and Energy-aware computing \and
  Green computing  \and Numerical weather  prediction \and Atmospheric
  chemistry  \and  Aerosols  modelling  \and  Profiling  methods  \and
  Benchmark    analysis   \and    COSMO-ART    coupled   model    \and
  Time-to-solution \and Energy-to-solution \and Manycore}
% \PACS{PACS code1 \and PACS code2 \and more}
% \subclass{MSC code1 \and MSC code2 \and more}
\end{abstract}

@@

\section{The COSMO-ART model system}
\label{sec:1}
\input{Sec1:COSMO-ART.tex}

\section{Experimental setup}
\label{sec:2}
\input{Sec2:Experimental-setup.tex}

\section{Evaluation}
\label{sec:3}
\input{Sec3:Evaluation.tex}

\section{Related work}
\label{sec:4}
\input{Sec4:Related.tex}

@@

\begin{acknowledgements}
This  research  was  supported   by  the  Exa2Green  research  project
co-funded  under the  EU  7th Framework  Program  Future and  Emerging
Technologies (FET) Proactive Initiative: Minimising Energy Consumption
of Computing  to the Limit  (MINECC).  We also  gratefully acknowledge
the  High  Performance  and  High  Productivity  Computing  Initiative
(\url{www.hp2c.ch}) for  results that will be  leveraged in subsequent
code refactoring.
\end{acknowledgements}

>>>>

\keywords{High performance computing  \and Energy-aware computing \and
  Green computing  \and Numerical weather  prediction \and Atmospheric
  chemistry  \and  Aerosols  modelling  \and  Profiling  methods  \and
  Benchmark    analysis   \and    COSMO-ART    coupled   model    \and
  Time-to-solution \and Energy-to-solution \and Xeon processor}
% \PACS{PACS code1 \and PACS code2 \and more}
% \subclass{MSC code1 \and MSC code2 \and more}
\end{abstract}

@@

\section{Related work}
\label{sec:1}
\input{Sec1:Related.tex}

\section{The COSMO-ART model system}
\label{sec:2}
\input{Sec2:COSMO-ART.tex}

\section{Power-performance measurement framework}
\label{sec:3}
\input{Sec3:Measurement-framework.tex}

\section{Evaluation}
\label{sec:4}
\input{Sec4:Evaluation.tex}

@@

\begin{acknowledgements}
The research  leading to these  results is supported by  the Exa2Green
project  co-financed by  the European  Commission under  7th Framework
Programme Future and Emerging Technologies (FET) Proactive Initiative:
Minimising Energy  Consumption of Computing to the  Limit (MINECC). We
also gratefully acknowledge the High Performance and High Productivity
Computing  Initiative  (\url{www.hp2c.ch}) for  results  that will  be
leveraged in subsequent code refactoring.
\end{acknowledgements}
